Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-07 arxiv/proof_examples.tex
revise

& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} +\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\

@@

Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(A)$ and its partial expectation. %$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}$.
 \begin{claim}\label{claim_largedev1}
 In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{1/2+e_1} \left(\sigma^2 + \kappa^2+d^2 \right) $$
for any small constant $e_1>0$.
	 \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
 \end{claim}
 \begin{proof}
By Fact \ref{lem_minv} (iii), we have that with high probability,
 \be\label{op_X12}
\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, 
 \ee
 and
 \be\label{op_Sig1}
\| \Sigma(A)^{-1}\|\le \frac1{A^2((\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}})+((\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}) }\lesssim \frac{1}{(A^2+1)p},
 \ee
 where we also used that $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$ for a small constant $\tau>0$.

>>>>

= &\left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)\right\|^2 +\left\| X^{(2)} \Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} (A\beta_1-A^2\beta_2)\right\|^2  \\
& + \exarg{\epsilon^{(1)}}{(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}} \\
&+\exarg{ \epsilon^{(2)}}{(\epsilon^{(2)})^\top \left(X^{(2)}\Sigma(A)^{-1} (X^{(2)})^\top-\id_{n_2}\right)^2\epsilon^{(2)}}   \\

@@

Using the concentration estimates in Lemma \ref{largedeviation}, we can control the difference between $g(A)$ and its partial expectation. %$\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{g(A) \mid X_1, X_2 ,\beta_1,\beta_2}$.
 \begin{claim}\label{claim_largedev1}
 In the setting of Proposition \ref{cor_MTL_loss}, we have that with high probability,
$$\left| g(A) - \exarg{\epsilon^{(1)}, \epsilon^{(2)} ,\beta_1,\beta_2}{g(A) \mid X_1, X_2 }\right| \le p^{1/2+c} \left(\sigma^2 + \kappa^2+d^2 \right) $$
for any small constant $c>0$.
	 \HZ{use consistent $e_1, e_2, e$, etc. Why not just use $\e$? Don't create too many different symbols. It's bad style..}
 \end{claim}
 \begin{proof}
By Fact \ref{lem_minv} (iii), we have that with high probability,
 \be\label{op_X12}
\|X^{(1)}\|\le \sqrt{(\sqrt{n_1} + \sqrt{p})^2 + n_1 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, \quad \|X^{(2)}\|\le \sqrt{(\sqrt{n_2} + \sqrt{p})^2 + n_2 \cdot p^{-c_{\varphi}}}\lesssim \sqrt{p}, 
 \ee
 and
 \be\label{op_Sig1}
\| \Sigma(A)^{-1}\|\le \frac1{A^2((\sqrt{n_1} - \sqrt{p})^2 - n_1 \cdot p^{-c_{\varphi}})+((\sqrt{n_2} - \sqrt{p})^2 - n_2 \cdot p^{-c_{\varphi}}) }\lesssim \frac{1}{(A^2+1)p},
 \ee
 where we also used that $1+\tau\le \rho_1\le \tau^{-1}$ and $1+\tau\le \rho_2\le \tau^{-1}$ for a small constant $\tau>0$.
